Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal

### 2020-08-29 Papers/02_Pulses_Envelope/PulsesEnvelope.tex
improvements in the images for the paper

\documentclass{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{amsmath}
\DeclareMathOperator{\sign}{sign}
\bibliography{bibli}

@@

\section{Results}

Applying the method to a diverse set of sound waves, we can have an idea of its generality.
% Revisit purpose and methods
% Overview of results
% Key results in details

>>>>

\documentclass{article}
% \usepackage{svg}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{amsmath}
\DeclareMathOperator{\sign}{sign}
\bibliography{bibli}

@@

\section{Results}
% TODO
Figure \ref{fig:FullFrontiers} illustrates the frontiers obtained by the application of the method to 6 diverse discrete sound waves.
% Revisit purpose and methods
% Overview of results
% Key results in details

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{07FullFrontiers.pdf}
  \caption{Positive and negative frontiers of 6 digital waves. For each wave, the region highlighted in black is shown in detail. For each wave the horizontal axis is the sample number $i$, while the vertical axis is the normalized amplitude. All 6 waves were recorded at 44100 $ \mathit{fps} $.}
  \label{fig:FullFrontiers}
\end{figure}
